An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-09-15 EconGrowth.Rnw
Deleted test text.
Reran Iran cases with the full algorithm for all resampling.
Completed fixing the rbind.fill bug.

% small change to test GitHub.

@@

<<setup, echo=FALSE, message=FALSE, eval=TRUE>>=
require(lattice)
require(latticeExtra)
require(ggplot2)
require(car)
require(mosaic)
require(xtable)
require(nlmrt)
require(micEconCES)
# Provides access to data melting. 
# See http://cran.r-project.org/web/packages/reshape2/reshape2.pdf
require(reshape2) 
# tikz allows use of LaTeX formatting and font in graphs. 
# Allows for a consistent look across the paper.
# See http://r-forge.r-project.org/R/?group_id=440 for instructions 
# on installing tikzDevice.
# require(tikzDevice) 
trellis.par.set(theme=theme.mosaic())
options(width=75)
options(show.signif.stars=TRUE)
opts_chunk$set(
  # ********************************************************
  eval=TRUE,
  # ********************************************************
  # tikz allows LaTeX code in graphical output. 
  # E.g., "$y$" for a variable name in the legend for a graph.  
  # dev='tikz',
  tidy=FALSE,
  comment=NA,
  # Tells whether to cache output from chunks are saved. Cacheing saves time. 
  # However, references to LaTeX tables DO NOT WORK if cacheing is turned on.
  cache=FALSE,
  warning=FALSE,  #Tells whether to show warnings in the output.
  # Turns off messages for all chunks. 
  # Set TRUE on an individual chunk to see it.
  message=FALSE, 
  # Tells whether to echo code for all chunks. 
  # Set TRUE on an individual chunk to see its code.
  echo=FALSE     
)
source("Econ-Growth-Functions2.R")
source("Graphics.R")
@

@@

Points on paper so far
1. Does the relative small differences in fit between different production functions warrant 
such a large debate on validity of one vs other? Clearly not. 
CD been used by economists for ease of use and extreme flexibility (Miller).  
PF generally used on instrumentalist grounds if give reasonable good description of data. 
NK econ theory provide poor causal explanation of observed data, 
but yet CD shows very good fit (miller, p17). 
CES is  more general, but is a liability in forecasting because difficult 
to get estimate of EoS that is consistent across studies (Miller, p26). 
Aggregation is problem of both CD and CES functional forms, 
so being careful when making strong inferences that cannot be justified.

>>>>

@@

<<setup, echo=FALSE, message=FALSE, eval=TRUE>>=
require(lattice)
require(latticeExtra)
require(ggplot2)
require(car)
require(mosaic)
require(xtable)
require(nlmrt)
require(micEconCES)
require(plyr)
# Provides access to data melting. 
# See http://cran.r-project.org/web/packages/reshape2/reshape2.pdf
require(reshape2) 
# tikz allows use of LaTeX formatting and font in graphs. 
# Allows for a consistent look across the paper.
# See http://r-forge.r-project.org/R/?group_id=440 for instructions 
# on installing tikzDevice.
# require(tikzDevice) 
trellis.par.set(theme=theme.mosaic())
options(width=75)
options(show.signif.stars=TRUE)
opts_chunk$set(
  # ********************************************************
  eval=TRUE,
  # ********************************************************
  # tikz allows LaTeX code in graphical output. 
  # E.g., "$y$" for a variable name in the legend for a graph.  
  # dev='tikz',
  tidy=FALSE,
  comment=NA,
  # Tells whether to cache output from chunks are saved. Cacheing saves time. 
  # However, references to LaTeX tables DO NOT WORK if cacheing is turned on.
  cache=FALSE,
  warning=FALSE,  #Tells whether to show warnings in the output.
  # Turns off messages for all chunks. 
  # Set TRUE on an individual chunk to see it.
  message=FALSE, 
  # Tells whether to echo code for all chunks. 
  # Set TRUE on an individual chunk to see its code.
  echo=FALSE     
)
source("Econ-Growth-Functions2.R")
source("Graphics.R")
@

@@

Points on paper so far

1. Does the relative small differences in fit between different production functions warrant 
such a large debate on validity of one vs other? Clearly not. 
CD been used by economists for ease of use and extreme flexibility (Miller).  
PF generally used on instrumentalist grounds if give reasonable good description of data. 
NK econ theory provide poor causal explanation of observed data, 
but yet CD shows very good fit (miller, p17). 
CES is  more general, but is a liability in forecasting because difficult 
to get estimate of EoS that is consistent across studies (Miller, p26). 
Aggregation is problem of both CD and CES functional forms, 
so being careful when making strong inferences that cannot be justified.
